Psychological Needs During Intergroup Contact

### 2022-01-05 Methods-and-Results.Rmd
general tbl added

```{r intergroupGeneralTbl, include=FALSE}
# Table of intergroup contact in ESM data:
# lm
#    #Contact
#     AvQual
#     #Contact*AvQual
# lme
#     OutgroupInteraction
#     NonOutgroupInteraction

@@

summ(mdlWorker$lmAttFreqQualX)

@@

names(mdlTblGeneralLmer) <- make.unique(names(mdlTblGeneralLmer))
mdlTblGeneral <-
  merge(mdlTblGeneralLm,
        mdlTblGeneralLmer %>% 
          mutate(coef = gsub("R2Marg_R2Cond", "R2_R2_adjusted", coef)),
        by = "coef",
        all = TRUE) 
names(mdlTblGeneral) <- make.unique(names(mdlTblGeneral))
mdlTblGeneral <- mdlTblGeneral %>%
  arrange(match(coef, c(
    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique %>% setdiff(., "(Intercept)"),
    names(mdlPrepGeneral[[1]]$random),
    "Groups",
    names(mdlPrepLmGeneral[[1]]$fit),
    setdiff(names(mdlPrepGeneral[[1]]$fit), c(names(mdlPrepLmGeneral[[1]]$fit), "Groups"))
  ))) %>%
  replace(is.na(.), "")

@@

\input{Tables/mdlContactGeneral}
<!-- \input{Tables/mdlTheory} -->
\input{Tables/mdlTheorylong}
\input{Tables/mdlRobustness}

>>>>

```{r intergroupGeneralTblLong, include=FALSE}
# Table of intergroup contact in ESM data:
# lm
#    #Contact
#     AvQual
#     #Contact*AvQual
# lme
#     OutgroupInteraction
#     NonOutgroupInteraction

@@

# summ(mdlWorker$lmAttFreqQualX)

@@

names(mdlTblGeneralLmer) <- make.unique(names(mdlTblGeneralLmer))
names(mdlTblGeneralLmer) <- gsub("Beta", "ES", names(mdlTblGeneralLmer))
names(mdlTblGeneralLm) <- make.unique(names(mdlTblGeneralLm))
names(mdlTblGeneralLm) <- gsub("Eta2_partial", "ES", names(mdlTblGeneralLm))

#mdlTblGeneralLong <- 
  rbind(mdlTblGeneralLm %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "SumContactNL",
                                 "AvQuality",
                                 "SumContactNL:AvQuality",
                                 "R2_R2_adjusted"
                               )
                             ),
                           mdlTblGeneralLmer %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "OutgroupInteraction",
                                 "NonOutgroupInteraction",
                                 "R2Marg_R2Cond"
                               )
                             )) %>%
    replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Intergroup General",
    #format = "latex",
    linesep = "",
    booktabs = TRUE,
    col.names = c("", rep(c("$B$", "Effect Size"), (ncol(.)-1)/2)),
    align = c("l", rep("c", ncol(.) - 1)),
    escape = FALSE,
    digits = 3
  )  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Study 1" = 2,
      "Study 2" = 2,
      "Study 3" = 2
    )
  ) %>%
  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5) %>%
  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  kableExtra::landscape() %>%
  save_kable("Tables/mdlContactGeneralLong.tex")
```

```{r intergroupGeneralTblWide, include=FALSE}
mdlTblGeneral <-
  merge(mdlTblGeneralLm,
        mdlTblGeneralLmer %>% 
          mutate(coef = gsub("R2Marg_R2Cond", "R2_R2_adjusted", coef)),
        by = "coef",
        all = TRUE) 
names(mdlTblGeneral) <- make.unique(names(mdlTblGeneral))
mdlTblGeneral <- mdlTblGeneral %>%
  arrange(match(coef, c(
    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique %>% setdiff(., "(Intercept)"),
    names(mdlPrepGeneral[[1]]$random),
    "Groups",
    names(mdlPrepLmGeneral[[1]]$fit),
    setdiff(names(mdlPrepGeneral[[1]]$fit), c(names(mdlPrepLmGeneral[[1]]$fit), "Groups"))
  ))) %>%
  replace(is.na(.), "")

@@

\input{Tables/mdlContactGeneral}
\input{Tables/mdlContactGeneralLong}
<!-- \input{Tables/mdlTheory} -->
\input{Tables/mdlTheorylong}
\input{Tables/mdlRobustness}
